Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-21 Paper/paper.tex
Getting rid of todo list
Have image for effect of KRG

\usepackage{todonotes}

@@

% New commands------------------------
\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}
\newcommand{\todoVK}[1]{\todo[color=blue!20]{#1}}

@@

If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.

Using the above and the previous observation this implies:

\begin{itemize}
    \item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
    \item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
\end{itemize}

A graphical proof of the lemma is then shown in Figure \ref{proof}.

\begin{figure}[!hbtp]
\begin{center}
\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
\end{center}
\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
\end{figure}

Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}

>>>>

@@

% New commands------------------------
\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}

@@

Let \(\bar \lambda_{\NH} = \bar \lambda_{\NH}(K_{\RG})\) be the effective arrival rate at NH.
If \(\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)},\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}\) then this implies that \(\bar \lambda_{\NH}(K_{\RG}) \geq \bar \lambda_{\NH}(K_{\RG} + 1)\) as shown in Figure \ref{fig:effect_of_KRG_on_arrival_rate}.

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,8}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
\end{figure}

Based on the previous observation this in turn implies:

\begin{equation}
    U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)
    \label{equ:UNH_as_a_function_of_KRG}
\end{equation}

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), we have:

\begin{equation}
    U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)
    \label{equ:UNH_as_a_function_of_KNH}
\end{equation}

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,8}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
\end{figure}

%If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
%Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.

%Using the above and the previous observation this implies:

%\begin{itemize}
    %\item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
    %\item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
%\end{itemize}

%A graphical proof of the lemma is then shown in Figure \ref{proof}.

%\begin{figure}[!hbtp]
%\begin{center}
%\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
%\end{center}
%\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
%\end{figure}

%Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
%As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
%As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
%Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}
